### 2017-05-15 Publications/Original Software Publications/Science of Computer Programming/reply letter/letter.tex
updating reply letter
Signed-off-by: Felipe R. Monteiro <rms.felipe@gmail.com>

    \begin{quote}
    \textcolor{blue}{\textbf{Response:} \textcolor{red}{Lucas: what would be the next step to reduce the number of thread interleavings? Improve MPOR? You can mention that we intend to use Abstract Interpretation to further reduce the model and the number of threads. Then you can cite our TACAS 2017 paper}}
    \end{quote}

>>>>

    \begin{quote}
    \textcolor{blue}{\textbf{Response:} We intend to use Abstract Interpretation to further reduce the number of thread interleavings (i.e., the model to be verified).}
    \end{quote}
